Revisiting Multi-Domain Machine Translation

### 2020-08-27 2020/tacl2020/multidomain.tex
removed a typo

In the second (\domain{new}), we assess [P5-UNK] by translating sentences from a domain unseen in training (\domain{news}).\fyDone{i would use RND / UNK rather than OLD / NEW} For each sentence, we automatically predict the most likely domain tag and use it for decoding.\footnote{\revision{To automatically predict domain tags, we train a language model in each domain and assign tag on a per-sentence basis based the language model log-probability (assuming uniform domain priors). Our domain classifier has an average prediction error of 16.4\% for in-domain data.}}
% Results are in the rightmost column of Table~\ref{tab:redomains}.
In this configuration, again, systems using domain tags in the inference step perform poorly, significantly worse than the \system{Mixed-Nat} baseline (Bleu=23.5)\fyDone{performance drop is now measured against Mixed-nat (leave it clearer?)}, sometimes by a large margin.\fyDone{Check significance, To be completed}t

>>>>

In the second (\domain{new}), we assess [P5-UNK] by translating sentences from a domain unseen in training (\domain{news}).\fyDone{i would use RND / UNK rather than OLD / NEW} For each sentence, we automatically predict the most likely domain tag and use it for decoding.\footnote{\revision{To automatically predict domain tags, we train a language model in each domain and assign tag on a per-sentence basis based the language model log-probability (assuming uniform domain priors). Our domain classifier has an average prediction error of 16.4\% for in-domain data.}}
% Results are in the rightmost column of Table~\ref{tab:redomains}.
In this configuration, again, systems using domain tags in the inference step perform poorly, significantly worse than the \system{Mixed-Nat} baseline (Bleu=23.5)\fyDone{performance drop is now measured against Mixed-nat (leave it clearer?)}, sometimes by a large margin.\fyDone{Check significance, To be completed}
